Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-13 longoutput.tex
Work on longoutput

\subsection{Picking universal gate set}

@@

\subsection{Creating Real Circuits}

Now consider a circuit $C=U_T\ldots U_1$, where $U_i\in\set{H, \Lambda(P(i))}$. Its input is classical $x$ of size $n$. Let $\ket\psi$ denote the initial state with $N$ qubits, containing $x$ possibly followed by ancilliaries.

We first reduce it to real gates and states only. The proof is taken from \cite{quant-ph/0301040}.

We consider the transform $\mathcal{F}(\ket{\phi})=\ket{0}\otimes\Re\ket{\phi}+\ket{1}\otimes\Im\ket{\phi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. We apply it to $\ket\psi$.

The transform commutes with Hadamard gates on the respective qubit, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position. We modify the circuit as appropriate to obtain $C'$ that has size $T'\leq 4T$. Its initial state is real, and all the gates are real. Which implies all the intermediate states as well as the output are real. Its input $x$ doesn't change, but the initial state $\ket{\psi'}$ is now size $N+1$.

We prove a theorem about this circuit that we'll use later.

@@

After these transformations, let $x$ be the new circuit input, and $U_T...U_1$ be the circuit to evaluate. Let $x_i$ denote the $i$th bit of $x$, and $|x|$ denote the number of the qubits in the circuit.

We then attempt to construct a local Hamiltonian with ground state that encodes the history of the computation: $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.

First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
As it is a sum of projections, $H_{clock}\geq 0$. We also show that $H_{clock}\in\spn\mathcal{G}_{XZ}$.
$$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
This can be checked by fixing the first and last qubit, then doing induction on the number of switches.

Then, we ensure that the initial condition is set up correctly.
$$H_{in}=\sum_i^{|x|}(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
$$H_{in}=\frac{1}{4}\sum_{i=1}^{|x|}(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$

>>>>

\subsection{Preprocessing circuit}

@@

Now consider a circuit $C=U_T\ldots U_1$ with the following properties:
\begin{itemize}
	\item $U_i\in\set{H, \Lambda(P(i))}$
	\item Has initial state $\ket\psi$ with $n$ qubits
\end{itemize}

We first reduce it to use only real gates and states. The proof is taken from \cite{quant-ph/0301040}. We consider the transform
$$\mathcal{F}(\ket{\phi})=\ket{0}\otimes\Re\ket{\phi}+\ket{1}\otimes\Im\ket{\phi}$$
where $\Re$ and $\Im$ denote real and imaginary parts respectively. It has the following properties

\begin{itemize}
	\item $\forall\ket\phi$, $\mathcal{F}(\ket\phi)$ is real.
	\item Preserves $X$ and $Z$ measurement results
\end{itemize}

We now apply $\mathcal{F}$ to $\ket\psi$. To make the notation easier, let $\ket{\psi}$ be 1-indexed, and the $\mathcal{F}\ket{\psi}$ be 0-indexed, so corresponding qubits stay in the same position.

The transform commutes with Hadamard gates on the respective qubit, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$
We modify the circuit as appropriate to obtain $C'$ that has size $T'\leq 4T$. We prove a theorem about this circuit that we'll use later.

@@

Let $C$ be a circuit with the above properties. Define the following quantities.
\begin{itemize}
	\item $C=U_T\ldots U_1$
	\item Let $x$ be the circuit input. Which is classical.
	\item Let $y$ denote the initial state. That is, $x$ possibly concatenated with ancillaries.
	\item Let $y_i$ denote the $i$-th bit of $y$
	\item Let $n=|y|$ be the number of qubits in $C$
\end{itemize}

We then attempt to construct a local Hamiltonian with the following ground state that encodes the history of the computation: $$\psi_{circuit}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{PhysRevA.78.012352}.

First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
As a sum of projections, clearly $H_{clock}\geq 0$. We shall also show that $H_{clock}\in\spn\mathcal{G}_{XZ}$.
$$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
This can be checked by fixing the first and last qubit, then doing induction on the number of switches.

Then, we ensure that the initial condition is set up correctly.
$$H_{in}=\sum_{i=1}^{|y|}(I-\ket{y_i}\bra{y_i})\otimes\ket{0}\bra{0}_1$$
The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
$$H_{in}=\frac{1}{4}\sum_{i=1}^{|y|}(I-(-1)^{y_i}Z_i)\otimes(I+Z_1)$$
